\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-07 chapters/1_intro.tex
Update figures; start getting rid of update rules

We evaluate the performances of these different agglomerative clustering algorithms on image instance segmentation of 2D urban scenes (CityScapes dataset) and 3D biological image stacks (CREMI neuron segmentation challenge), by comparing achieved scores, efficiency and robustness to noisy edge weights. \TODO{Chapters description}

\begin{figure}[t]
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=\textwidth]{./figs/intro_image.pdf} % left bottom right top
\caption{
{\small (\textbf{a}) Some iterations of the generalized algorithm on toy graphs with attractive (green) and repulsive (red) interactions. (\textbf{b}) Example of CREMI 2016 data \cite{cremiChallenge} overlaid with instance segmentation. (\textbf{c}) Agglomeration order, representing which pairs of neighboring pixels were merged first (blue) and later on (red).
We note how similar update rules, like \emph{Sum} (in the middle) and \emph{Mean} (on the right), lead to strongly different merging orders. 
% On the left: a single cluster is returned with only attractive interactions.
}
 % main ideas and contributions
\label{fig:intro_figure}}
\end{figure}

>>>>

We evaluate the performances of these different agglomerative clustering algorithms on image instance segmentation of 2D urban scenes (CityScapes dataset) and 3D biological image stacks (CREMI neuron segmentation challenge), by comparing achieved scores, efficiency and robustness to noisy edge weights. 
% \TODO{Chapters description}

\begin{figure}[t]
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=\textwidth]{./figs/intro_image.pdf} % left bottom right top
\caption{
 (\textbf{a}) Some iterations of the generalized algorithm on toy graphs with attractive (green) and repulsive (red) interactions. (\textbf{b}) Example of CREMI 2016 neuron-segmentation data \cite{cremiChallenge} overlaid with instance segmentation. (\textbf{c}) Agglomeration order, representing which pairs of neighboring pixels were merged first (white), later on (brown) or never (black).
We note how similar linkage criteria, like \emph{Sum} (in the middle) and \emph{Average} (on the right), lead to strongly different merging orders. 
% On the left: a single cluster is returned with only attractive interactions.
 % main ideas and contributions
\label{fig:intro_figure}}
\end{figure}

### 2019-05-07 chapters/3_algorithm.tex
Update figures; start getting rid of update rules

\paragraph{Inter-cluster interaction}\label{par:linkage_criterion_def} We call two clusters $S_1,S_2$ \emph{adjacent} if there exists at least one edge ${e_{uv}\in E}$ connecting a node $u\in S_1$ to a node $v\in S_2$. In agglomerative HC, the interaction $\interact_{S_1,S_2}$ between two clusters $S_1, S_2$ is usually defined as a function, named \emph{linkage criterion}, depending on the weights of all edges connecting clusters $S_1$ and $S_2$. For example, for a \emph{maximum} linkage criterion statistic (single-linkage), the inter-cluster interaction is given by:
\begin{equation}\label{eq:max_linkage}
\interact_{S_1,S_2} = \, \max_{e\in U} \cost(e), \qquad \text{where}\quad U = \{ e_{uv} \in E | u \in S_1, \, v \in S_2 \}.
\end{equation}
Other common choices are \emph{minimum} (complete linkage) or \emph{average} (average linkage). %and \emph{sum}.
% \begin{equation}
%  \text{$S_1, S_2 \in \Pi$ are \emph{adjacent}} \quad \Longleftrightarrow  \quad  \mathcal{B}(S_1,S_2) \equiv \{ e_{uv} \in E | u \in S_1, \, v \in S_2 \} \neq \emptyset
% \end{equation}
% where we defined the set of edges connecting two adjacent clusters as \UPDATE{\emph{boundary}} \UPDATE{$\mathscr{W}(S_1,S_2) , \mathcal{G}'_{\mathcal{G},\Pi}(V',E')$}.  in the boundary $\mathcal{B}(S_1,S_2)$. Some examples of linkage criterion statistics are \emph{maximum} (single-linkage), \emph{minimum} (complete-linkage) and average (average-linkage).

@@

\begin{figure}
        \centering
        \begin{minipage}{0.49\textwidth}
\centering
        % \includegraphics[width=\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
        \includegraphics[width=\textwidth]{./figs/edge_contraction.pdf} % left bottom right top
\captionof{figure}{ 
{\small Example of edge contraction. First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (violet bars). Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$. In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$. In step iii), double edges $e_{tu}$ and $e_{tv}$ resulting from edge contraction are replaced by single edge with updated interaction $f(\tilde{\cost}(e_{tu}), \tilde{\cost}(e_{tv}))$, see definitions in Tab.~\ref{tab:linkage-criteria}. }
\label{fig:edge_contraction_and_contr_graph}  }
    \end{minipage}\hspace{0.01\textwidth}
    \begin{minipage}{0.49\textwidth}
        \centering
\includegraphics[width=0.91\textwidth]{./figs/add_constraints.pdf}
\captionof{figure}{ 
{\small Some iterations of the generalized algorithm  with (top) and without (bottom) adding cannot-link constraints. The graph has both attractive (green) and repulsive (red) edges; cannot-link constraints are given by violet bars. At each iteration, the edge selected by the algorithm is highlighted in yellow. When cannot-link constraints are enforced, the final clustering is given by two clusters instead of only one.}
\label{fig:algorithm_with_without_CLC}}
    \end{minipage}
\end{figure}

\begin{algorithm}[t]
  \caption{Generalized Algorithm for Signed Graphs Agglomerative Clustering}
   \hspace*{\algorithmicindent} \textbf{Inputs:} Graph $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes; boolean variable {\color{blue}\texttt{addCannotLink}}  \\
  \hspace*{\algorithmicindent} \textbf{Outputs:} Final clustering $\Pi$\\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]
    % \Procedure{SignedGraphEdgeContr}{{\color{blue}bool \emph{addConstraints}}}
      % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
      \State Initialize clustering $\Pi=\{\{v_1\}, \ldots, \{v_N\}\}$ and contracted graph $\tilde{\mathcal{G}}_\Pi \gets \mathcal{G}$
      \State Initialize \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$
      \State Sort edges in priority queue (PQ) in descending order of priority $|\cost_e|=|w^+_e - w^-_e|$ 
      \State
      \While{PQ is \textbf{not} empty}
        \State Pop edge $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ with highest absolute interaction $|\tilde{\cost}|$
        \If{({\color{ForestGreen}\textbf{$\tilde{\cost} > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
          % \State PQ, $\,E_\dagger,\,\, E' \gets$ \textsc{deleteDoubleEdges}($u,v$)
        %   \State Update costs of double edges;
        %   \State Propagate constrained flags of double edges;
          \State Contract $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and merge the two clusters $S_u,S_v \in \Pi$
          \For{every new pair of double edges $(e_1,e_2)$ in $\tilde{\mathcal{G}}_\Pi$}
            % \State Get costs $\cost_1, \cost_2$ of $e_1,e_2$
            \State Delete $e_2$ from $\tilde{\mathcal{G}}_\Pi$ and update priority of $e_1$ with rule $f(\tilde{\cost}_{e_1},\tilde{\cost}_{e_2})$ defined in Tab. \ref{tab:linkage-criteria} 
            % \Statex \hspace{\algorithmicindent}\hspace{\algorithmicindent}\hspace{\algorithmicindent}\hspace{\algorithmicindent} update priority of $e_1$
            % \State Delete $e_2$ from $\mathcal{G}'$
          \EndFor
          % \State  Replace double edges in $\mathcal{G}'$ with single edges
          % \Statex \hspace{\algorithmicindent}\hspace{\algorithmicindent}\hspace{\algorithmicindent} and update priorities
        \EndIf
        % \State
        \If{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLink}}}
          % \State Flag $e_{uv}$ as MustNotLink
          \State \texttt{canBeMerged}$[e_{uv}] \gets$ \texttt{False}
        \EndIf
      \EndWhile
      % \For{$e  \in E$ in descending order of absolute costs $|W(e)|$}
      %   \If{({\color{ForestGreen}\textbf{$W(e) > 0$}}) \textbf{AND} (edge is not constrained)}
      %     \State Contract edge $e$ in the graph $\mathcal{G}'$;
      %     \State Update costs of double edges;
      %     \State Propagate constrained flags of double edges;
      %     % \For{every new double edge}
      %     %   \State Delete double edges
      %     %   \State Insert new one with updated cost
      %     % \EndFor
      %   \EndIf
      %   \If{({\color{red}\textbf{$W(e) \leq 0$}}) \textbf{AND} ({\color{blue}\emph{addConstraints}})}
      %     \State Flag edge $e$ as constrained
      %   \EndIf
      % \EndFor
      % \State
      \State
      \Return $\Pi$
      % \State

@@

  \end{algorithmic}
  \label{main_alg}
\end{algorithm}

@@

\begin{table*}
    \centering
    \scriptsize
    \begin{subtable}[t!]{\textwidth}\centering
        \begin{tabular}{r  l || c | c | c}
            % \toprule\toprule
            \multicolumn{2}{c||}{}  &   & \multicolumn{2}{c}{\textbf{Signed graphs}}  \\        
            % \cmidrule(l{.15em}){4-5}
            % \cline{4-5}
            \multicolumn{2}{c||}{} & \textbf{Unsigned graphs} &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\        
             &  &  &  \thead{\textsc{No}} & \thead{\textsc{Yes}} \\        
            % \cmidrule[0.3em]{3-5}
            % \midrule[0.15em]
            \midrule\midrule
            Sum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \tilde{\cost}_1+\tilde{\cost}_2$} & \thead{Sum Linkage\\Hier. Aggl. Clust.} & \thead{Greedy Additive \\ Edge Contraction \cite{keuper2015efficient}} & \thead{Greedy Fixation\\\cite{levinkov2017comparative}} \\ \midrule

            \makecell[r]{Absolute \\Max:} & \thead[l]{
            $
            f(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
            \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
            \tilde{\cost}_2 & \text{otherwise}
             \end{cases} 
            $}
               & \thead{Single Linkage\\Hier. Aggl. Clust. \cite{lance1967general}} & \thead{Mutex Watershed \\\cite{wolf2018mutex}} & \thead{Mutex Watershed\\\cite{wolf2018mutex}} \\ \midrule
            \makecell[r]{Mean:} & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \mathrm{weightAvg}\{ \tilde{\cost}_1, \tilde{\cost}_2 \} $}                                 & \thead{ Average Linkage\\ Hier. Aggl. Clust. \cite{lance1967general}} & \thead{Average Linkage\\Signed Aggl. Clust. (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule

            Max: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \max \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $}                                 & \thead{Single Linkage\\Hier. Aggl. Clust. \cite{lance1967general}} & \thead{Single Linkage \\Signed Aggl. Clust. (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule

            Min:& \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \min \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $}                                 & \thead{Complete Linkage\\ Hier. Aggl. Clust. \cite{lance1967general}}  & \thead{Complete Linkage \\Signed Aggl. Clust. (\textbf{NEW})} & \thead{\textbf{NEW}}

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{{\small The table lists the tested update rules $f$. Existing and new algorithms are given by a specific choice of update rule, type of graph (signed or unsigned) and optional use of cannot-link constraints.}}
    \label{tab:linkage-criteria}
\end{table*}

>>>>

\paragraph{Inter-cluster interaction}\label{par:linkage_criterion_def} We call two clusters $S_1,S_2$ \emph{adjacent} if there exists at least one edge ${e_{uv}\in E}$ connecting a node $u\in S_1$ to a node $v\in S_2$. In agglomerative HC, the interaction $\interact_{S_1,S_2}$ between two clusters $S_1, S_2$ is usually defined as a function, named \emph{linkage criterion}, depending on the weights of all edges connecting clusters $S_1$ and $S_2$. For example, for a \emph{maximum} linkage criterion statistic (single-linkage), the inter-cluster interaction is given by:
\begin{equation}\label{eq:max_linkage}
\interact_{S_1,S_2} = \, \max_{e\in U(S_u,S_v)} \cost(e), \qquad \text{where}\quad E_{12} = \{ e_{uv} \in E | u \in S_1, \, v \in S_2 \}.
\end{equation}
Other common choices are \emph{minimum} (complete linkage) or \emph{average} (average linkage). %and \emph{sum}.
% \begin{equation}
%  \text{$S_1, S_2 \in \Pi$ are \emph{adjacent}} \quad \Longleftrightarrow  \quad  \mathcal{B}(S_1,S_2) \equiv \{ e_{uv} \in E | u \in S_1, \, v \in S_2 \} \neq \emptyset
% \end{equation}
% where we defined the set of edges connecting two adjacent clusters as \UPDATE{\emph{boundary}} \UPDATE{$\mathscr{W}(S_1,S_2) , \mathcal{G}'_{\mathcal{G},\Pi}(V',E')$}.  in the boundary $\mathcal{B}(S_1,S_2)$. Some examples of linkage criterion statistics are \emph{maximum} (single-linkage), \emph{minimum} (complete-linkage) and average (average-linkage).

@@

\begin{figure}
\centering
        \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth]{./figs/example_no_constr.pdf}
        \caption{No constraints}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth]{./figs/example_with_constr.pdf}
        \caption{With constraints}
    \end{subfigure}
\caption{Some iterations of the generalized algorithm with and without adding cannot-link constraints. In this example the \emph{Sum} linkage criteria was used. The graph has both attractive (green) and repulsive (red) edges and cannot-link constraints are shown with triple violet bars on the edges. We note that when constraints are enforced, the final clustering is given by two clusters instead of only one.}
\label{fig:algorithm_with_without_CLC}
\end{figure}
\begin{algorithm}[t]
  \caption{Generalized Algorithm for Signed Graphs Agglomerative Clustering}
   \hspace*{\algorithmicindent} \textbf{Inputs:} Graph $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes; boolean variable {\color{blue}\texttt{addCannotLink}}  \\
  \hspace*{\algorithmicindent} \textbf{Outputs:} Final clustering $\Pi$\\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]
    % \Procedure{SignedGraphEdgeContr}{{\color{blue}bool \emph{addConstraints}}}
      % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
      \State Initialize clustering $\Pi=\{\{v_1\}, \ldots, \{v_N\}\}$ and contracted graph $\tilde{\mathcal{G}}_\Pi \gets \mathcal{G}$
      \State Initialize \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$
      \State Sort edges in priority queue (PQ) in descending order of priority $|\cost_e|=|w^+_e - w^-_e|$ 
      \State
      \While{PQ is \textbf{not} empty}
        \State Pop edge $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ with highest absolute interaction $|\tilde{\cost}|$
        \If{({\color{ForestGreen}\textbf{$\tilde{\cost} > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
          % \State PQ, $\,E_\dagger,\,\, E' \gets$ \textsc{deleteDoubleEdges}($u,v$)
        %   \State Update costs of double edges;
        %   \State Propagate constrained flags of double edges;
          \State Contract $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and merge the two clusters $S_u,S_v \in \Pi$
          \For{every new pair of double edges $(e_1,e_2)$ in $\tilde{\mathcal{G}}_\Pi$}
            % \State Get costs $\cost_1, \cost_2$ of $e_1,e_2$
            \State Delete $e_2$ from $\tilde{\mathcal{G}}_\Pi$ and update priority of $e_1$ with rule $f(\tilde{\cost}_{e_1},\tilde{\cost}_{e_2})$ defined in Tab. \ref{tab:linkage-criteria} 
            % \Statex \hspace{\algorithmicindent}\hspace{\algorithmicindent}\hspace{\algorithmicindent}\hspace{\algorithmicindent} update priority of $e_1$
            % \State Delete $e_2$ from $\mathcal{G}'$
          \EndFor
          % \State  Replace double edges in $\mathcal{G}'$ with single edges
          % \Statex \hspace{\algorithmicindent}\hspace{\algorithmicindent}\hspace{\algorithmicindent} and update priorities
        \EndIf
        % \State
        \If{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLink}}}
          % \State Flag $e_{uv}$ as MustNotLink
          \State \texttt{canBeMerged}$[e_{uv}] \gets$ \texttt{False}
        \EndIf
      \EndWhile
      % \For{$e  \in E$ in descending order of absolute costs $|W(e)|$}
      %   \If{({\color{ForestGreen}\textbf{$W(e) > 0$}}) \textbf{AND} (edge is not constrained)}
      %     \State Contract edge $e$ in the graph $\mathcal{G}'$;
      %     \State Update costs of double edges;
      %     \State Propagate constrained flags of double edges;
      %     % \For{every new double edge}
      %     %   \State Delete double edges
      %     %   \State Insert new one with updated cost
      %     % \EndFor
      %   \EndIf
      %   \If{({\color{red}\textbf{$W(e) \leq 0$}}) \textbf{AND} ({\color{blue}\emph{addConstraints}})}
      %     \State Flag edge $e$ as constrained
      %   \EndIf
      % \EndFor
      % \State
      \State
      \Return $\Pi$
      % \State

@@

  \end{algorithmic}
  \label{main_alg}
\end{algorithm}

@@

\begin{table*}
    \centering
    \scriptsize
    \begin{subtable}[t!]{\textwidth}\centering
        \begin{tabular}{c r  l ?? c | c | c}
            % \toprule\toprule
            \multicolumn{3}{c??}{}  & \multirow{2}{*}[-0.5em]{\textbf{Unsigned Graphs}} & \multicolumn{2}{c}{\textbf{Signed Graphs}}  \\        
            % \cmidrule(l{.15em}){4-5}
            % \cline{4-5}
            % \multicolumn{2}{c||}{} &  &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\        
            \multicolumn{3}{c??}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\

            % \midrule[0.15em]
            \cmidrule[0.15em]{2-6}\morecmidrules \cmidrule[0.15em]{2-6}
            % \midrule \midrule
            \multirow{5}{*}[-2.5em]{\begin{turn}{90}\thead{\textbf{Linkage criteria} $\,\,\interact_{S_u ,S_v}$}\end{turn}}  & Sum: & $\displaystyle \sum_{e\in (S_u \times S_v)} \cost_e$ & \thead{Sum Linkage\\Hier. Aggl. Clust.} & \thead{Greedy Additive \\ Edge Contraction \cite{keuper2015efficient}} & \thead{Greedy Fixation\\\cite{levinkov2017comparative}} \\ 
            \cmidrule[0.07em]{2-6}

             &\makecell[r]{Absolute \\Max:} & 
            $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in (S_u \times S_v)} |\cost_t|$
               & \thead{Single Linkage\\Hier. Aggl. Clust. \cite{lance1967general}} & \thead{Mutex Watershed \\\cite{wolf2018mutex}} & \thead{Mutex Watershed\\\cite{wolf2018mutex}} \\
              \cmidrule[0.07em]{2-6}
             & \makecell[r]{Average:} & $\displaystyle \sum_{e\in (S_u \times S_v)} \cost_e \bigg/ \big|S_u \times S_v\big|  $ & \thead{ Average Linkage\\ Hier. Aggl. Clust. \cite{lance1967general}} & \thead{Average Linkage\\Signed Aggl. Clust. (\textbf{NEW})} & \thead{\textbf{NEW}}\\ 
            \cmidrule[0.07em]{2-6}
           % \midrule

            & Max: & $\displaystyle \max_{e\in (S_u \times S_v)} \cost_e$ & \thead{Single Linkage\\Hier. Aggl. Clust. \cite{lance1967general}} & \thead{Single Linkage \\Signed Aggl. Clust. (\textbf{NEW})} & \thead{\textbf{NEW}}\\ 
            \cmidrule[0.07em]{2-6}

            & Min:& $\displaystyle \min_{e\in (S_u \times S_v)} \cost_e$ & \thead{Complete Linkage\\ Hier. Aggl. Clust. \cite{lance1967general}}  & \thead{Complete Linkage \\Signed Aggl. Clust. (\textbf{NEW})} & \thead{\textbf{NEW}}

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{{\small The table lists the tested linkage criteria. Existing and new algorithms are given by a specific choice of linkage criteria, type of graph (signed or unsigned) and optional use of cannot-link constraints.}}
    \label{tab:linkage-criteria}
\end{table*}

% \begin{table*}
%     \centering
%     \scriptsize
%     \begin{subtable}[t!]{\textwidth}\centering
%         \begin{tabular}{r  l || c | c | c}
%             % \toprule\toprule
%             \multicolumn{2}{c||}{}  &   & \multicolumn{2}{c}{\textbf{Signed graphs}}  \\        
%             % \cmidrule(l{.15em}){4-5}
%             % \cline{4-5}
%             \multicolumn{2}{c||}{} & \textbf{Unsigned graphs} &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\        
%              &  &  &  \thead{\textsc{No}} & \thead{\textsc{Yes}} \\        
%             % \cmidrule[0.3em]{3-5}
%             % \midrule[0.15em]
%             \midrule\midrule
%             Sum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \tilde{\cost}_1+\tilde{\cost}_2$} & \thead{Sum Linkage\\Hier. Aggl. Clust.} & \thead{Greedy Additive \\ Edge Contraction \cite{keuper2015efficient}} & \thead{Greedy Fixation\\\cite{levinkov2017comparative}} \\ \midrule

%             \makecell[r]{Absolute \\Max:} & \thead[l]{
%             $
%             f(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
%             \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
%             \tilde{\cost}_2 & \text{otherwise}
%              \end{cases} 
%             $}
%                & \thead{Single Linkage\\Hier. Aggl. Clust. \cite{lance1967general}} & \thead{Mutex Watershed \\\cite{wolf2018mutex}} & \thead{Mutex Watershed\\\cite{wolf2018mutex}} \\ \midrule
%             \makecell[r]{Mean:} & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \mathrm{weightAvg}\{ \tilde{\cost}_1, \tilde{\cost}_2 \} $}                                 & \thead{ Average Linkage\\ Hier. Aggl. Clust. \cite{lance1967general}} & \thead{Average Linkage\\Signed Aggl. Clust. (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule

%             Max: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \max \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $}                                 & \thead{Single Linkage\\Hier. Aggl. Clust. \cite{lance1967general}} & \thead{Single Linkage \\Signed Aggl. Clust. (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule

%             Min:& \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \min \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $}                                 & \thead{Complete Linkage\\ Hier. Aggl. Clust. \cite{lance1967general}}  & \thead{Complete Linkage \\Signed Aggl. Clust. (\textbf{NEW})} & \thead{\textbf{NEW}}

%         \end{tabular}
%         % \caption{Linkage criteria}
%     \end{subtable} 
%     \caption{{\small The table lists the tested update rules $f$. Existing and new algorithms are given by a specific choice of update rule, type of graph (signed or unsigned) and optional use of cannot-link constraints.}}
%     \label{tab:linkage-criteria}
% \end{table*}

### 2019-05-07 chapters/5_experiments_compare_rules.tex
Update figures; start getting rid of update rules

@@

\subsection{Evaluating different update rules} \label{sec:exp_first_comparison}
\begin{itemize}
  \item Highlight difference of the sum in Fig. \ref{fig:intro_figure}
  \item compare different choices of signed-cost-mappings (say which one worked best)
  \item present cremi crop-C table and rule out single and complete linkage
\end{itemize}

>>>>

\begin{figure}[t]
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=\textwidth]{./figs/comparison.pdf} % left bottom right top
\caption{
{\small Comparison of results from different update rules on signed graph with and without cannot-link constraints 
}
 % main ideas and contributions
\label{fig:cremi_comparison}}
\end{figure}
\begin{figure}[b]
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=\textwidth]{./figs/cityscapes_compare.pdf} % left bottom right top
\caption{
{\small Comparison of results from different update rules on signed graph with and without cannot-link constraints 
}
 % main ideas and contributions
\label{fig:cytiscapes_comparison}}
\end{figure}

@@

\subsection{Evaluating different update rules} \label{sec:exp_first_comparison}
\begin{itemize}
  \item Highlight difference of the sum in Fig. \ref{fig:intro_figure}
  % \item compare different choices of signed-cost-mappings (say which one worked best)
  \item present cremi crop-C table and rule out single and complete linkage
\end{itemize}

### 2019-05-07 chapters/5_experiments_noise.tex
Update figures; start getting rid of update rules

        \caption{Merge-biased noise added to edge weights} \label{fig:thresh}
    \end{subfigure}%
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.35in 0.65in 0.80in,clip]{./figs/split_noise.pdf}
        \caption{Split-biased noise added to edge weights} \label{fig:ws}
    \end{subfigure}

\caption{{\small Rand-Scores achieved by the generalized algorithm and different update rules when noise is added to the edge weights. Solid lines represent median values; values between the 25th and the 75th percentile are shown in shade areas. In the plots at the top, long-range connections are not used.}}\label{fig:noise_plots}
\end{figure}

@@

\begin{minipage}[T!]{\textwidth}
        \centering
        \begin{minipage}{0.45\textwidth}
\centering

        \includegraphics[width=0.85\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}

    \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise. Blue pixels represent boundary evidence. Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}). 
    %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
    %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
    }
    \label{fig:noisy_affs}
    \end{minipage}\hspace{0.04\textwidth}
\begin{minipage}{0.48\textwidth}
% \begin{table}
    \centering
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{l M{0.25\textwidth} M{0.25\textwidth}}
        \toprule
        & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
        Update rule: & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{Mean}& \textbf{0.343}  & 0.339  \\
GMIS \cite{liu2018affinity} & 0.341 & -  \\
Max &   0.243  &   0.325  \\
Abs. Max. \cite{wolf2018mutex}  & -  & 0.321 \\
Sum \cite{levinkov2017comparative} & 0.313  & 0.319  \\
Min &  0.000    & 0.000  \\
        \end{tabular}
        % \caption{Linkage criteria}
    % \end{subtable} 
    \captionof{table}{AP scores on the cityscapes validation set for the generalized algorithm and different types of update rules.  }
    \label{tab:results_cityscapes}
\end{minipage}
\end{minipage}

>>>>

        \caption{Merge-biased noise added to edge weights} \label{fig:thresh}
    \end{subfigure}%
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.35in 0.65in 0.80in,clip]{./figs/split_noise.pdf}
        \caption{Split-biased noise added to edge weights} \label{fig:ws}
    \end{subfigure}
\caption{{\small Rand-Scores achieved by the generalized algorithm and different update rules when noise is added to the edge weights. Solid lines represent median values; values between the 25th and the 75th percentile are shown in shade areas. In the plots at the top, long-range connections are not used.}}\label{fig:noise_plots}
\end{figure}

@@

\begin{figure}
        \centering
\begin{minipage}[T]{0.48\textwidth}
% \begin{table}
    \centering
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{l M{0.2\textwidth} M{0.2\textwidth}}
        \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \multicolumn{1}{c}{\thead{No\\Constraints}} & \multicolumn{1}{c}{\thead{With\\constraints}} \\ \midrule
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{Mean}& \textbf{0.9292}  & 0.8647  \\
% Lifted multicut & - & -  \\
Abs. Max.  & 0.9246 & 0.9246 \\
Max &   0.0611  &  0.9208  \\
Sum  & 0.8377  & 0.8426  \\
Min &  0.0737 & 0.0779  \\
        \end{tabular}
        % \caption{Linkage criteria}
    % \end{subtable} 
    \captionof{table}{Arand-Scores on CREMI challenge (crop of sample C) \UPDATE{for the generalized algorithm and different types of linkage criteria and the optional use of cannot-link constraints.} }
    \label{tab:results_cremi_val}
\end{minipage}\hfill
\begin{minipage}[T]{0.48\textwidth}
% \begin{table}
    \centering
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{l M{0.25\textwidth} M{0.25\textwidth}}
        \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \multicolumn{1}{c}{\thead{No\\Constraints}} & \multicolumn{1}{c}{\thead{With\\constraints}} \\ \midrule
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{Mean}& \textbf{0.343}  & 0.339  \\
GMIS \cite{liu2018affinity} & 0.330 & -  \\
Max &   0.243  &   0.325  \\
Abs. Max.  & 0.321 & 0.321 \\
Sum & 0.313  & 0.319  \\
Min &  0.000    & 0.000  \\
        \end{tabular}
        % \caption{Linkage criteria}
    % \end{subtable} 
    \captionof{table}{AP scores on the cityscapes validation set for the generalized algorithm and different types of linkage criteria.  }
    \label{tab:results_cityscapes}
\end{minipage}
\end{figure}
